### 2021-04-29 sections/queueing_model/main.tex
Add paragraph for transition rates

The model consists of two types of individuals; class 1 and class 2.
Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Class 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed to the next waiting zone only when the number of 
individuals in the next system (in waiting zone 1 and in service) is less than a 
pre-determined threshold \(T\).
When the threshold is reached, all class 2 individuals that arrive will remain 
\textit{``blocked''} in the buffer centre until the number of people in the 
system is reduced below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.

@@

>>>>

The model consists of two types of individuals; class 1 and class 2.
Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Class 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed to the next waiting zone only when the number of 
individuals in the next system (in waiting zone 1 and in service) is less than a 
pre-determined threshold \(T\).
When the threshold is reached, all class 2 individuals that arrive will remain 
\textit{``blocked''} in the buffer centre until the number of people in the 
system is reduced below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

\begin{itemize}
    \item $\lambda_1$: The arrival rate of class 1 individuals
    \item $\lambda_2$: The arrival rate of class 2 individuals
    \item $\mu$: The service rate for individuals receiving service in waiting 
    zone 1
    \item $C$: The number of servers
    \item $T$: The threshold where class 2 individuals will start being blocked 
\end{itemize}

@@

Note that $\Lambda$ here denotes the overall arrival rate in the model by both 
classes of individuals (i.e. $\Lambda = \lambda_1 + \lambda_2$). 
A visualisation of how the transition rates relate to the states of the model 
can be seen in the general Markov chain model shown in figure 
\ref{fig:general-markov-model}.
